\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
few changes in the intro, description of the generic algo, changed decide to commit, \mathcal{C} to \mathcal{D}

We show that the core idea underlying EPaxos can be captured in an abstract algorithm that uses two abstractions: (1), a per-command dependency-set computation algorithm, a concept that we define in the paper, and (2), an algorithm ensuring, for each command proposed to it, agreement on a dependency set. Both abstractions lend themselves well to implementations that avoid the use of a unique leader process.

@@

We prove that all the algorithms in the family are safe and live, and we have formalized our ideas in TLA+ and thoroughly model-check our claims with the TLC model-checker.

@@

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network. Processes in $P$ must solve the Generalized Consensus problem~\cite{Lamport05GeneralizeConsensus}. Each process receives proposals for commands of the form $\opn{Propose}(c)$, and must produce responses of the form $\opn{Decide}(\sigma)$, where $\sigma$ is a c-struct. 
The sequence of calls observed must satisfy the non-triviality, consistency, stability, and liveness properties described below.
We refer the reader to~\cite{Lamport05GeneralizeConsensus}, and we use the same notation, for the definition of c-structs and generalized consensus. Briefly, the c-structs are a set of elements, including $\bot$, with an operator $\bullet$ for appending commands to a c-struct. C-structs are partially ordered: $\sigma_1\sqsubseteq \sigma_2$ iff there exists a sequence of commands $cs$ such that $\sigma_2 = \sigma_1\bullet cs$ and $\bot\sqsubseteq \sigma$ for any
$\sigma$. Two c-structs are compatible when they have a
common upper bound. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands. The consistency property of generalized consensus requires that any two decided c-structs be compatible.

We now present our abstract leaderless generalized consensus algorithm.
A process $p$ receiving a command $c$ proceeds in three phases. First, it calls a \textit{dependency-set} sub-algorithm (\Cref{dep-algo}) to determine a set of commands $cs$ \todo{are we sure about the notation cs?} that the command $c$ may depend on. Second, the process $p$ proposes the mapping  $c\mapsto cs$ to a \textit{map-agreement} sub-algorithm (\Cref{map-algo}); the map-agreement sub-algorithm may subsequently commit a mapping $c\mapsto cs'$ for $c$, in which case $cs'$ becomes the set of dependencies of $c$, and we say that $c$ is executable when its dependency set is empty or when all its dependencies are executable. 
Finally, when $c$ is executable, the process $p$ may execute $c$ by deciding the c-struct obtained by running the \emph{graph-processing} algorithm described in \Cref{abstract-algo}.
Any other process can run the three phases independently of $p$ and eventually execute the command despite a crash of $p$.
However, we show that a leaderless  generalized consensus algorithm is always safe and is live when its underlying dependency-set and map-agreement algorithms are safe and live.
The leaderless generalized consensus algorithm orchestrates the two dependency-set and map-agreement sub-algorithms as shown in \cref{fig:deps-set-algo3}.\todo{This pseudocode must be in figure (a). Also we have to better describe the pseudocode.}

@@

\todo{Why not add the decide call to the interface, in order to guarantee liveness?}

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, and \todo{this is not clear: an input interface $\opn{decide}\left( c,\mathcal{D} \right)$ (meant to receive inputs from the agreement sub-algorithm)}, where $p\in P$ is the process executing the call.
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$), if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
    \item If a suggestion $\opn{suggest}_p(c,\mathcal{D})$ has been made and no input $\opn{decide}_q\left( c,\mathcal{D'} \right)$ is observed, then eventually a new suggestion $\opn{suggest}_r\left( c,\mathcal{D''} \right)$ for $r\neq p$ is made.
\end{enumerate}

@@

		\begin{algorithmic}[1]
			{\scriptsize
			\START[$\opn{init}_p$]{{\bf upon}}{$()$}
			\State $m_p\gets \emptyset$
			\State $\sigma_p\gets \bot$
			\END
			\START[$\opn{GC-propose}_p$]{{\bf upon}}{$(c)$}
			\State {\bf call} $\opn{announce}_p\left( c \right)$
			\END
			\Statex
			\START[$\opn{suggest}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $\opn{propose}_p( c,\mathcal{D})$ 			
			\END
			\Statex
			\START[$\opn{decide}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $m_p \gets m_p \oplus \left[ c \mapsto \mathcal{D}\right]$	
			\State $\sigma_p \gets  \opn{c-struct}\left(m_p\right)$
			\State $\opn{GC-decide}_p(\sigma_p)$		
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo3}
}
\caption{Example of dependency-set algorithm and leaderless generalized consensus implementations.}
\label{fig:deps-set-algo}
\end{figure*}

@@

A map-agreement algorithm exposes the input interface $\opn{propose}_p\left( c, \mathcal{D} \right)$, to propose a set of dependencies $\mathcal{D}$ for a command $c$, and the output interface $\opn{decide}_p\left( c, \mathcal{D} \right)$, to decide $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.
Moreover, a map-agreement algorithm must ensure that: 
\begin{comment}
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $\mathcal{D}$ is decided for a command $c$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item If $\mathcal{D}_1$ is decided for a command $c$ and $\mathcal{D}_2$ is decided for the same command $c$, then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
 \end{enumerate}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item For any decision $\opn{decide}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item For any two decisions $\opn{decide}_p\left( c, \mathcal{D}_1 \right)$, $\opn{decide}_q\left( c, \mathcal{D}_2 \right)$ (with $p$ possibly equal to $q$), then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.

@@

The graph processing algorithm is executed locally by a node (line 10 of \cref{fig:deps-set-algo3}). It must compute the value of $\opn{c-struct}\left( g_p \right)$, as defined in \cref{lindef}.
Its key property is \cref{lemma1}. 
We assume that processes initially agree, for each set of commands $cs$, on a total order $<_{cs}$ on $cs$.
In practice, if commands are attached a unique identifier among a totally ordered set, $<_{cs}$ can be the restriction of this total order on $cs$.

%\textbf{Local dependency graph computed by a process.} 
We say that a command $c$ in the domain of $m_p$ is \emph{complete} when no command $c$ which is not in the domain of $m_p$ can be reached from $c$ by recursively following $c$'s dependencies.
The local variable $m_p$ denotes a directed graph $g_p$ whose set of vertices $V\left( g_p \right)$ is the complete commands of $m_p$ and whose edges $E\left( g_p \right)$ are such that there is an edge from $c_1$ to $c_2$ iff $c_2 \in m_p\left[ c_1 \right]$ (i.e., $c_1$ depends on $c_2$). For example, if $m_p = \left[ c_1 \mapsto \aset{c_2,c_4}, c_2 \mapsto \aset{c_3}, c_3 \mapsto \aset{c_2}\right]$ then $V\left( g_p \right) = \aset{c_2,c_3}$ and $E\left( g_p \right) = \aset{\left( c_2,c_3 \right),\left( c_3,c_2 \right)}$.

%\textbf{Orders induced by a graph.}
A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $c_1 \preceq_g c_2$ iff there is a path from $c_1$ to $c_2$ and none from $c_2$ to $c_1$.
%Let $\opn{TOs}\left( g \right)$ be the set of total orders $o$ such that $\preceq_g \subseteq o$.
For example, consider $h$ where $V\left( h \right)=\aset{c_1,c_2,c_3,c_4}$ and $E\left( h \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right),\left( c_1,c_3 \right)}$. 
We have that $\preceq_h = \aset{\left( c_1,c_3 \right)}$.
%If $c\in V\left( g \right)$, we write $\left[ c \right]_g$ for the strongly connected component of $g$ to which $c$ belongs. 
%\textbf{Linearizations of a dependency graph.}
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every $c_1,c_2\in V\left( g \right)$, $c_1 \preceq_g c_2$ implies $c_1 \ll c_2$, and if $c_1$ and $c_2$ belong to the same strongly connected component $cs$ and $ c_1 <_{cs} c_2$ hold, then $c_1 \ll c_2$. For example, assuming that $c_2 \leq_{\aset{c_1,c_2}} c_1$, the linearizations of $h$ are $\aseq{c_2,c_1,c_3,c_4}$, $\aseq{c_2,c_1,c_4,c_3}$, $\aseq{c_2,c_4,c_1,c_3}$, and $\aseq{c_4,c_2,c_1,c_3}$.
%\textbf{Partial order on graphs.}

@@

\textbf{Linearization function.} Consider a function $f$ mapping sets of commands to sequences of commands such that $f\left[ cs \right]$ is a total order on the set $cs$.

@@

Consider a function $f$ mapping sets of commands to sequences of commands such that $f\left[ cs \right]$ contains each command in $cs$ exactly once.
A sequence of commands $cseq$ is an $f$-linearization of the graph $g$ if and only there is a sequence whose element of strongly connected

@@

A c-struct set is a set containing the element $\bot$ and with an append operator $\bullet$ such that $\sigma \bullet c$ is a c-struct, for any c-struct $\sigma$ and command $c$. 
We also write the $\sigma\bullet\aseq{c_1,\cdots,c_n}$ for the c-struct $\sigma\bullet c_1\bullet\cdots\bullet c_n$.
C-structs are partially ordered by the relation $\sqsubseteq$ defined such that $\sigma_1\sqsubseteq\sigma_2$ iff there exists a sequence of commands $cs$ such that $\sigma_2=\sigma_1\bullet cs$. Two c-structs are compatible when they have a common upper bound; when this is the case, two c-structs $\sigma_1$ and $\sigma_2$ have a least upper bound, noted $\bigsqcup\left( \sigma_1,\sigma_2 \right)$.
We say that two commands \textit{commute} when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $, for every c-struct $\sigma$. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands (see~\cite{Lamport05GeneralizeConsensus} for a complete discussion on c-struct). 
In the rest of the paper the symbol $c$, possibly sub-scripted, ranges over commands, and the symbol $\mathcal{D}$, possibly sub-scripted, ranges over sets of commands.

We can now state the generalized-consensus properties: non-triviality requires that any decided c-struct be of the form $\bot\bullet cs$, where $cs$ is a sequence of proposed commands; consistency requires than any two decided c-structs $\sigma_1$ and $\sigma_2$ be compatible; stability requires that when a process $p$ decides a c-struct $\sigma_1$ and time $t_1$ and $\sigma_2$ at time $t_2$, then $t_1 \leq t_2$ implies that $\sigma_1\sqsubseteq \sigma_2$; finally, liveness requires that
if a command keeps beeing proposed, then a c-struct $\sigma$ containing the command is eventually decided.

>>>>

We show that the core idea underlying EPaxos can be captured in a generic algorithm that uses two abstractions: (1), a per-command dependency-set computation algorithm, a concept that we define in the paper, and (2), an algorithm ensuring, for each command proposed to it, agreement on a dependency set. Both abstractions lend themselves well to implementations that avoid the use of a unique leader process.

@@

We prove that all the algorithms in the family are safe and live, and we have formalized our ideas in TLA+ and have thoroughly model-checked our safety claims with the TLC model-checker.

@@

We consider a set of processes $P$ subject to crash-stop faults and communicating by message-passing in an asynchronous network. Processes in $P$ must solve the Generalized Consensus problem~\cite{Lamport05GeneralizeConsensus}. Each process receives proposals for commands of the form $\opn{Propose}(c)$, and must produce responses of the form $\opn{Decide}(\sigma)$, where $\sigma$ is a c-struct. 
The sequence of calls observed must satisfy the non-triviality, consistency, stability, and liveness properties described below.
We refer the reader to~\cite{Lamport05GeneralizeConsensus}, and we use the same notation, for the definition of c-structs and generalized consensus. Briefly, the c-structs are a set of elements, including $\bot$, with an operator $\bullet$ for appending commands to a c-struct. C-structs are partially ordered: $\sigma_1\sqsubseteq \sigma_2$ iff there exists a sequence of commands $\mathcal{D}$ such that $\sigma_2 = \sigma_1\bullet \mathcal{D}$ and $\bot\sqsubseteq \sigma$ for any
$\sigma$. Two c-structs are compatible when they have a
common upper bound. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands. The consistency property of generalized consensus requires that any two decided c-structs be compatible.

We now present our abstract leaderless generalized consensus algorithm.
A process $p$ receiving a command $c$ proceeds in three phases. First, it calls a \textit{dependency-set} sub-algorithm (\Cref{dep-algo}) to determine a set of commands $\mathcal{D}$ that the command $c$ may depend on. Second, $p$ proposes the mapping  $c\mapsto \mathcal{D}$ to a \textit{map-agreement} sub-algorithm (\Cref{map-algo}); the map-agreement sub-algorithm may subsequently commit a mapping $c\mapsto \mathcal{D}'$ for $c$, in which case $\mathcal{D}'$ becomes the dependency set of $c$;
we say that $c$ is executable when all its transitive dependencies are known. %no command $c'$ for which no mapping has been committed is reachable from $c$ by recursively following committed mappings. 
\todo{Change the name of the the decide action to commit.}
Finally, when $c$ is executable, the $p$ may execute $c$ by deciding the c-struct obtained by \emph{locally} running a \emph{graph-processing} algorithm described in \Cref{abstract-algo}.
Any other process can run the three phases independently of $p$ and eventually execute the command despite a crash of $p$.
However, we show that a leaderless  generalized consensus algorithm is always safe and is live when its underlying dependency-set and map-agreement algorithms are safe and live.
The leaderless generalized consensus algorithm orchestrates the two dependency-set and map-agreement sub-algorithms as shown in \cref{fig:deps-set-algo3}.\todo{This pseudocode must be in figure (a). Also we have to better describe the pseudocode.}

@@

A dependency-set algorithm exposes the input interface $\opn{announce}_p\left( c \right)$, to announce a command $c$, the output interface $\opn{suggest}_p \left( c,\mathcal{D}\right)$, to suggest a set of dependencies $\mathcal{D}$ for $c$, and \todo{this is not clear: an input interface $\opn{commit}\left( c,\mathcal{D} \right)$ (meant to receive inputs from the agreement sub-algorithm)}, where $p\in P$ is the process executing the call.
Moreover, a dependency-set algorithm must ensure that:
\begin{enumerate}[noitemsep,nolistsep]
    \item For any suggestion $\opn{suggest}_p \left( c,\mathcal{D}\right)$, every command in $\{c\}\cup \mathcal{D}$ must have been announced before.
    \item For any two suggestions $\opn{suggest}_p \left( c_1,\mathcal{D}_1\right)$ and $\opn{suggest}_q \left( c_2,\mathcal{D}_2\right)$ (with $p$ possibly equal to $q$), if $c_1$ and $c_2$ do not commute then either $c_1\in \mathcal{D}_2$ or $c_2 \in \mathcal{D}_1$.
    \item If a suggestion $\opn{suggest}_p(c,\mathcal{D})$ has been made and no input $\opn{commit}_q\left( c,\mathcal{D'} \right)$ is observed, then eventually a new suggestion $\opn{suggest}_r\left( c,\mathcal{D''} \right)$ for $r\neq p$ is made.
\end{enumerate}

@@

		\begin{algorithmic}[1]
			{\scriptsize
			\START[$\opn{init}_p$]{{\bf upon}}{$()$}
			\State $m_p\gets \emptyset$
			\State $\sigma_p\gets \bot$
			\END
			\START[$\opn{GC-propose}_p$]{{\bf upon}}{$(c)$}
			\State {\bf call} $\opn{announce}_p\left( c \right)$
			\END
			\Statex
			\START[$\opn{suggest}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $\opn{propose}_p( c,\mathcal{D})$ 			
			\END
			\Statex
			\START[$\opn{commit}_p$]{{\bf upon}}{$(c,\mathcal{D})$}
			\State  $m_p \gets m_p \oplus \left[ c \mapsto \mathcal{D}\right]$	
			\State $\sigma_p \gets  \opn{c-struct}\left(m_p\right)$
			\State $\opn{GC-decide}_p(\sigma_p)$		
			\END
			}
		\end{algorithmic}
	\end{varwidth}%
}
\label{fig:deps-set-algo3}
}
\caption{Example of dependency-set algorithm and leaderless generalized consensus implementations.}
\label{fig:deps-set-algo}
\end{figure*}

@@

A map-agreement algorithm exposes the input interface $\opn{propose}_p\left( c, \mathcal{D} \right)$, to propose a set of dependencies $\mathcal{D}$ for a command $c$, and the output interface $\opn{commit}_p\left( c, \mathcal{D} \right)$, to commit $\mathcal{D}$ for $c$, where $p\in P$ is the process executing the call.
Moreover, a map-agreement algorithm must ensure that: 
\begin{comment}
\begin{enumerate}[noitemsep,nolistsep]
    \item If the set of dependencies $\mathcal{D}$ is committed for a command $c$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item If $\mathcal{D}_1$ is committed for a command $c$ and $\mathcal{D}_2$ is committed for the same command $c$, then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.
 \end{enumerate}

@@

\begin{enumerate}[noitemsep,nolistsep]
    \item For any decision $\opn{commit}_p\left( c, \mathcal{D} \right)$, then $\mathcal{D}$ has been proposed for $c$ at an earlier time.
    \item For any two decisions $\opn{commit}_p\left( c, \mathcal{D}_1 \right)$, $\opn{commit}_q\left( c, \mathcal{D}_2 \right)$ (with $p$ possibly equal to $q$), then $\mathcal{D}_1$ is equal to $\mathcal{D}_2$.

@@

The graph processing algorithm is executed locally by a node (line 10 of \cref{fig:deps-set-algo3}). It must compute the value of $\opn{c-struct}\left( g_p \right)$, as defined in \cref{lindef}.
Its key property is \cref{lemma1}. 
We assume that processes initially agree, for each set of commands $\mathcal{D}$, on a total order $<_{\mathcal{D}}$ on $\mathcal{D}$.
In practice, if commands are attached a unique identifier among a totally ordered set, $<_{\mathcal{D}}$ can be the restriction of this total order on $\mathcal{D}$.

%\textbf{Local dependency graph computed by a process.} 
We say that a command $c$ in the domain of $m_p$ is \emph{executable} when no command $c$ which is not in the domain of $m_p$ can be reached from $c$ by recursively following $c$'s dependencies.
The local variable $m_p$ denotes a directed graph $g_p$ whose set of vertices $V\left( g_p \right)$ is the executable commands of $m_p$ and whose edges $E\left( g_p \right)$ are such that there is an edge from $c_1$ to $c_2$ iff $c_2 \in m_p\left[ c_1 \right]$ (i.e., $c_1$ depends on $c_2$). For example, if $m_p = \left[ c_1 \mapsto \aset{c_2,c_4}, c_2 \mapsto \aset{c_3}, c_3 \mapsto \aset{c_2}\right]$ then $V\left( g_p \right) = \aset{c_2,c_3}$ and $E\left( g_p \right) = \aset{\left( c_2,c_3 \right),\left( c_3,c_2 \right)}$.

%\textbf{Orders induced by a graph.}
A directed graph $g$ \emph{induces a partial order} $\preceq_g$ on its vertices defined such that $c_1 \preceq_g c_2$ iff there is a path from $c_1$ to $c_2$ and none from $c_2$ to $c_1$.
%Let $\opn{TOs}\left( g \right)$ be the set of total orders $o$ such that $\preceq_g \subseteq o$.
For example, consider $h$ where $V\left( h \right)=\aset{c_1,c_2,c_3,c_4}$ and $E\left( h \right)=\aset{\left( c_1,c_2 \right),\left( c_2,c_1 \right),\left( c_1,c_3 \right)}$. 
We have that $\preceq_h = \aset{\left( c_1,c_3 \right)}$.
%If $c\in V\left( g \right)$, we write $\left[ c \right]_g$ for the strongly connected component of $g$ to which $c$ belongs. 
%\textbf{Linearizations of a dependency graph.}
We say that a total order $\ll$ on $V\left( g \right)$ is a \emph{linearization} of $g$ when for every $c_1,c_2\in V\left( g \right)$, $c_1 \preceq_g c_2$ implies $c_1 \ll c_2$, and if $c_1$ and $c_2$ belong to the same strongly connected component $\mathcal{D}$ and $ c_1 <_{\mathcal{D}} c_2$ hold, then $c_1 \ll c_2$. For example, assuming that $c_2 \leq_{\aset{c_1,c_2}} c_1$, the linearizations of $h$ are $\aseq{c_2,c_1,c_3,c_4}$, $\aseq{c_2,c_1,c_4,c_3}$, $\aseq{c_2,c_4,c_1,c_3}$, and $\aseq{c_4,c_2,c_1,c_3}$.
%\textbf{Partial order on graphs.}

@@

\textbf{Linearization function.} Consider a function $f$ mapping sets of commands to sequences of commands such that $f\left[ \mathcal{D} \right]$ is a total order on the set $\mathcal{D}$.

@@

Consider a function $f$ mapping sets of commands to sequences of commands such that $f\left[ \mathcal{D} \right]$ contains each command in $\mathcal{D}$ exactly once.
A sequence of commands $cseq$ is an $f$-linearization of the graph $g$ if and only there is a sequence whose element of strongly connected

@@

A c-struct set is a set containing the element $\bot$ and with an append operator $\bullet$ such that $\sigma \bullet c$ is a c-struct, for any c-struct $\sigma$ and command $c$. 
We also write the $\sigma\bullet\aseq{c_1,\cdots,c_n}$ for the c-struct $\sigma\bullet c_1\bullet\cdots\bullet c_n$.
C-structs are partially ordered by the relation $\sqsubseteq$ defined such that $\sigma_1\sqsubseteq\sigma_2$ iff there exists a sequence of commands $\mathcal{D}$ such that $\sigma_2=\sigma_1\bullet \mathcal{D}$. Two c-structs are compatible when they have a common upper bound; when this is the case, two c-structs $\sigma_1$ and $\sigma_2$ have a least upper bound, noted $\bigsqcup\left( \sigma_1,\sigma_2 \right)$.
We say that two commands \textit{commute} when $\sigma\bullet c_1\bullet c_2 =  \sigma\bullet c_2\bullet c_1 $, for every c-struct $\sigma$. Intuitively, a c-struct represents a set of sequences that are all equivalent up to the ordering of commutative commands (see~\cite{Lamport05GeneralizeConsensus} for a complete discussion on c-struct). 
In the rest of the paper the symbol $c$, possibly sub-scripted, ranges over commands, and the symbol $\mathcal{D}$, possibly sub-scripted, ranges over sets of commands.

We can now state the generalized-consensus properties: non-triviality requires that any decided c-struct be of the form $\bot\bullet \mathcal{D}$, where $\mathcal{D}$ is a sequence of proposed commands; consistency requires than any two decided c-structs $\sigma_1$ and $\sigma_2$ be compatible; stability requires that when a process $p$ decides a c-struct $\sigma_1$ and time $t_1$ and $\sigma_2$ at time $t_2$, then $t_1 \leq t_2$ implies that $\sigma_1\sqsubseteq \sigma_2$; finally, liveness requires that
if a command keeps beeing proposed, then a c-struct $\sigma$ containing the command is eventually decided.
